Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-26 journal/article.tex
T: Physical spaces, Agile material

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P29, P36, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

In some cases the old way of working had people seated physically distributed,
in opposite to what agile methods typically suggest. Office spaces needed to be
arranged so that the entire team could work in a single room, but it took time
and effort, and it was not always possible [P36, P6]. Lewis and Neher describe
how dedicated rooms for teams could not be arranged, and team events such as
daily stand-ups required booking a conference room [P29]. In another case the
estate organization shut down the teams' attempts to modify working spaces
[P49].

>>>>

Mentioning big bang versus step wise [P16].

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included investments in
some tangible entities. These investments were focused on enabling agile
software development. Typical investments were new management tools,
improvements in testing environments, and updating of the physical working
spaces. Table \ref{table:transformation_investments} summarizes the

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Activities in the organization aiming to create change}
    \label{table:transformation_investments}
\end{table}

% Organization specific agile material

A typical practice was creating some internal material promoting the new agile
model. The material served both a documenting role and promoted awareness for
the new development model. The material was created to help explaining the agile
model to stakeholders, and to serve as a reference for teams implemeting it.
Typical in-house agile material was a manual which presented the organization
specific implementations of agile practices [P1]. Many cases described using a
wiki-based website to maintain and distribute information on agile practices
[P14, P16, P45]. Hanly et al. [P23] describes how a n organization specific
cookbook for agile implementation was created. The cookbook resolved
misconceptions, presented differences between the old model and agile, and
described agile development in traditional terms [P23]. Other agile material
organizations produced were short videos [P32], and a branded theme for the new
process [P8]. One primary source provided the organization specific Agile Policy
as an appendix [P26].

% Physical spaces

In many cases it was mentioned that the work spaces needed to be rearranged to
better allow the team centric model of agile [P35, P42, P48]. The possibilities
to create a team area varied between cases. Some cases had trouble with physical
space arrangements [P36], in some cases spaces could be arranged with some
bargaining with the facilities department [P6, P38], but some organizations
invested readily in good facilities [P46]. In addition to the work areas some
organizations took the chance to improve common areas also [P22, P46].

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P29, P36, P38, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

In some cases the old way of working had people seated physically distributed,
in opposite to what agile methods typically suggest. Office spaces needed to be
arranged so that the entire team could work in a single room, but it took time
and effort, and it was not always possible [P6, P36, P38]. Lewis and Neher describe
how dedicated rooms for teams could not be arranged, and team events such as
daily stand-ups required booking a conference room [P29]. In another case the
estate organization shut down the teams' attempts to modify working spaces
[P49].
